Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
save files update
extend make_SR

  data %>%
    apriori(

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r clean_AR}
clean_AR <- function(AR){

  AR %>%
    as("data.frame") %>%

    # Exclude rules with no support
    filter(
      count >= 1
      ) %>%

    # separate rule
    mutate(
      rules = str_remove_all(rules, pattern = "[{]|[}]")
      ) %>%
    separate(
      rules,
      into = c("lhs", "rhs"), 
      sep  = " => "
      ) %>%

    # separate rhs and lhs
    separate(
      rhs,
      into    = c("rhs_course", "rhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      ) %>%
    separate(
      lhs,
      into    = c("lhs_course", "lhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      )

@@

The function `compute_support()` computes the support of the lhs and rhs of the rules.
```{r compute_support}
compute_metrics <- function(AR, data_support, type_rule){

@@

    # rhs.support
    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!enquo(type_rule)
      )

@@

  data %>%
    my_apriori %>%
    clean_AR %>%
    compute_metrics(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      )

@@

  my_apriori %>%
  clean_AR %>%

@@

      parameter = list(
        #include as many item sequences as possible
        support = 0,   # min support of a sequence
        maxsize = 1,   # max number of items of an element of a sequence
        maxlen  = 2,   # max number of element of a sequence
        mingap  = 1,   # min time difference between consecutive element of a sequence
        maxgap  = 1e4  # max time difference between consecutive element of a sequence
        #maxwin  = 1e4 # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
        ),

@@

```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame

clean_SR <- function(rules){

@@

```{r}
make_SR <- function(data){

  data %>%
    my_cspade %>%
    my_ruleInduction %>%
    clean_SR

@@

SR$taken <- sequences$taken %>%
  make_SR
```

@@

@@

>>>>

    apriori(

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe

```{r function clean_rules}
clean_rules <- function(rules){

@@

The function `compute_support()` computes the support of the lhs and rhs of the rules.
```{r compute_support}
compute_rhs.support <- function(AR, data_support, type_rule){

@@

    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!enquo(type_rule)
      )

@@

  data %>%
    my_apriori %>%
    clean_rules %>%
    compute_rhs.support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      )

@@

  my_apriori %>%
  clean_rules %>%

@@

      parameter = list(

        # only include subsequences of the type {one item} => {one item}
        maxlen  = 2,   # max length of sequence
        maxsize = 1,   # max number item for element

        # include all such subsequences
        support = 0,   # min suppor
        mingap  = 1,   # min time difference between consecutive element
        maxgap  = 1e4  # max time difference between consecutive element

        ),

@@

```{r}
make_SR <- function(data, data_support, type_rule){

  data %>%
    my_cspade %>%
    my_ruleInduction %>%
    clean_rules %>%
    compute_rhs.support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      )

@@

@@

SR$taken <- sequences$taken %>%
  make_SR(
    data_support = d_support$TNT, 
    type_rule = rate.take
  )
```

@@

  make_SR(
    data_support = d_support$PF_HL,
    type_rule = rate.fail
  ) %>%

@@

  make_SR(
    data_support = d_support$PF_HL,
    type_rule = rate.low
  ) %>%
